Measuring contrast processing in the visual system using SSVEP

### 2024-04-20 review.qmd
All figures now created before the main text

# all package loading and subfunctions defined here
import numpy as np
import matplotlib.pyplot as plt
from matplotlib import colormaps
import scipy as scp

@@

@@

```{python}

#| label: fig-sweepvep
#| fig-cap: "Sweep VEP simulation showing how a contrast detection threshold can be estimated from sweep VEP data measured at higher contrasts."
#| fig-cap-location: bottom

import matplotlib.pyplot as plt
from matplotlib import colormaps
import numpy as np
import scipy as scp
from sklearn.linear_model import LinearRegression

def simpleTransducerFunction(inputContrast, c50, RMax):
 # Here we model a simple hyperbolic ratio function. Also called a "Naka-Rushton" function.
 # RMax defines the reponse gain of the transducer (how big the biggest output is). 
 # c50 defines the conrast sensitivity. Smaller values are more sensitive.
 # The exponent can also vary - here we fix it to 2
  expnt=2
  output=RMax*(inputContrast**expnt)/(inputContrast**expnt + c50**expnt)
  return output

axs.set_title(f'Simulated sweep VEP at {nLevels} different contrasts', fontsize=10)
axs.semilogx(contrastRange, transducedSignal, 'o')
axs.semilogx(contrastRange[:4], reg.predict(X), 'r--', label='Linear Fit')
axs.semilogx([x_intercept], [0], 'ro', label='Threshold')
axs.set_xlabel('Contrast')
axs.set_ylabel('Amplitude (a.u.)')
axs.set_xlim(0.01, 1)
axs.set_ylim(0, 10)
axs.legend()
axs.grid()
plt.tight_layout()
plt.show()

@@

```{python}

#| label: fig-plotclinical
#| fig-cap: "Example contrast response functions for different clinical conditions. Panel (a) shows modelled contrast response functions for epilepsy patients (blue) and control participants (black), based on the data of Tsai et al. (2011). Panel (b) shows functions for the amblyopic (red) and fellow (black) eyes of adults with amblyopia, based on the data of Baker et al. (2015). Panel (c) shows functions for children with (green) and without (black) a diagnosis of autism, based on the data of Vilidaite et al. (2018). Panel (d) shows data from *Drosophila melanogaster* (fruit flies) from Afsari et al. (2014). One day-old flies expressing a human gene linked to Parkinson's (hLRRK-G2019S) show increased SSVEP response amplitude and sensitivity (red) compared to control animals (black)."
#| fig-cap-location: bottom

import numpy as np
import matplotlib.pyplot as plt

# To save the figure
# plt.savefig('Figures/clinicalplot.pdf')
plt.show()

>>>>

# all package loading and subfunctions defined here
import numpy as np
import matplotlib.pyplot as plt
from matplotlib import colormaps
import scipy as scp
from sklearn.linear_model import LinearRegression

@@

```{python makesweep}

axs.set_title(f'Simulated sweep VEP at {nLevels} different contrasts', fontsize=10)
axs.semilogx(contrastRange, transducedSignal, 'o')
axs.semilogx(contrastRange[:4], reg.predict(X), 'r--', label='Linear Fit')
axs.semilogx([x_intercept], [0], 'ro', label='Threshold')
axs.set_xlabel('Contrast')
axs.set_ylabel('Amplitude (a.u.)')
axs.set_xlim(0.01, 1)
axs.set_ylim(0, 10)
axs.legend()
axs.grid()
plt.tight_layout()
plt.savefig('Figures/sweepplot.pdf')

```{python makeclinicalplot}

# To save the figure
plt.savefig('Figures/clinicalplot.pdf')

@@

![Sweep VEP simulation showing how a contrast detection threshold can be estimated from sweep VEP data measured at higher contrasts.](Figures/sweepplot.pdf){#fig-sweepvep}

@@

![Example contrast response functions for different clinical conditions. Panel (a) shows modelled contrast response functions for epilepsy patients (blue) and control participants (black), based on the data of Tsai et al. (2011). Panel (b) shows functions for the amblyopic (red) and fellow (black) eyes of adults with amblyopia, based on the data of Baker et al. (2015). Panel (c) shows functions for children with (green) and without (black) a diagnosis of autism, based on the data of Vilidaite et al. (2018). Panel (d) shows data from *Drosophila melanogaster* (fruit flies) from Afsari et al. (2014). One day-old flies expressing a human gene linked to Parkinson's (hLRRK-G2019S) show increased SSVEP response amplitude and sensitivity (red) compared to control animals (black).](Figures/clinicalplot.pdf){#fig-plotclinical}
